### 2015-02-06 fundamentals/examples.tex
improve graphs - address many of katy's comments

\begin{enumerate}
    \item Once through (no recycle) 
    \item Modified open (1-pass recycle)
    \item closed (infinite-pass recycle)
\end{enumerate}

For each of these fuel cycles, a 1,100 month \Cyclus simulation with only a
single reactor is run in addition to a simulation with 10 reactors with
staggered refueling times.  As the number of staggered-cycle reactors
increases the system converges toward continuous material flow results.
\Cyclus flexibility allows this transition to be examined.  The facilities
used in these simulations are:

@@

    \item \textbf{Reactor} (\Class{cycamore::Reactor}): This is a reactor
        model that requests any number of input fuel types and uses static
        compositions to transmute them to after they are burnt and discharged
        from the core.  Due to the static spent fuel compositions spent fuel
        compositions become "incorrect" as the input fuel diverges from the
        fixed, expected input composition. The reactor was configured to model
        a light water reactor with a 3 batch core (20,000 kg HM per batch)
        operating on an 18 month cycle with a 2 month refuel time.  The
        reactor was also configured to take in either enriched UOX fuel or
        recycled MOX fuel - preferring the latter if available.

    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
        facility requests depleted uranium and separated fissile material and
        mixes them together into recycled MOX fuel that it offers to
        requesters.  The streams are mixed using a D-factors approach
        \TODO{add D-factors citation} in an attempt to match simple neutronics
        properties of an ideal target fuel composition.

@@

    \item \textbf{UOX Fabrication} (\Class{cycamore::Source}): This facility
        provides enriched UOX fuel as requested with infinite capacity.

    \item \textbf{DU Source} (\Class{cycamore::Source}): This facility provides
        depleted uranium as requested with infinite capacity.

@@

For the once through case, the \Class{Reactor} was set to offer all spent fuel
as waste.  For the modified open case, the \Class{Reactor} offerred spent UOX
into a spent fuel market where it is preferrentially sent to separations, but
spent MOX is still offerred as waste.  In the closed case, the \Class{Reactor}
offers all spent fuel into a spent fuel market. Because the separations
facility requests spent fuel with a higher preference than the repository, it
is sent there if possible.  All these preferences are easy to adjust and
\Cyclus will dynamically handle supply constraints and non-uniform preference
resolution.  It is notable that separations and recycle fuel fabrication
capacity is deployed identically in all simulations.  In the once-through
case, the recycling loop never acquires material, and so reactors always
receive fresh UOX fuel.  In the modified open case, the recycle loop only
acquires spent UOX.  The \gls{DRE} ensures everything operates smoothly in all
cases.

Cyclus' discrete materials make single-pass recycle easy to implement.  The
reactors keep track of fuel as discrete batches. A reactor remembers where it
received each batch from.  If a batch was received from the recycled fuel
fabrication facility, it does not offer it to separations and instead sends it
to the repository directly.  The material flows for the modified open case are
shown in Figure \ref{fig:flowmodopen}.

\begin{figure}[H]
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\caption{Modified open 1-pass \gls{MOX} recycle scenario material flows.}
\label{fig:flowmodopen}
\end{figure}

Changing the scenario from a modified open fuel cycle to a closed fuel cycle
requires only a one-word change in the input file regarding the output
commodity for the spent \gls{MOX} fuel of the \Class{Reactor}:

\begin{lstlisting}[language=diff]
     <fuel>         
       <incommodity>mox</incommodity>
  -    <outcommodity>waste</outcommodity>
  +    <outcommodity>spent_fuel</outcommodity>
       <inrecipe>mox_resh_fuel</inrecipe>
       <outrecipe>mox_spent_fuel</outrecipe>
     </fuel>
\end{lstlisting}

This results in the material flows in Figure \ref{fig:flowclosed}.  A
similarly trivial change was used to switch from the once through to a
modified open fuel cycle.  Note that the \Class{Reactor} always transmutes
fuel into fixed compositions, so nuclide-specific flows become
somewhat unrealistic in the fully closed cycle case.

@@

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
(no recycle), modified open, and closed (infinite-pass recycle) variations of
the one-reactor scenario described above. The figure was generated directly
from \Cyclus output data. After several batch cycles (near month 300) in the
modified open and closed cases, enough separated fissile material accumulates
in the fuel fabrication facility to generate a full recycled batch.  When this
batch is transmuted, more plutonium is burned than created.  This results in a
drop in the total fuel cycle system plutonium inventory.  This pattern repeats
roughly every 10 cycles (200 months) for the modified open case and every 9
cycles (180 months) for the closed case.  Because the modified open scenario
does not re-recycle material, it takes the fabrication facility 1 cycle longer
to accumulate a full batch of fissile material.

@@

Figure \ref{fig:puseriesn} shows plutonium buildup for the 10-reactor
simulations of the open, modified open, and closed scenarios.  As the number
of reactors (with staggered refueling) increases, the behavior of the system
approaches a more steady average reminiscent of continuous material flow
models.

>>>>

\begin{enumerate}
    \item Once through (no recycle) 
    \item 1-pass MOX recycle
    \item Infinite-pass MOX recycle
\end{enumerate}

For each of these fuel cycles, a 1,100 month single-reactor \Cyclus simulation
was run in addition to a 10-reactor simulation with staggered refueling times.
As the number of staggered-cycle reactors increases the system converges
toward continuous material flow results.  \Cyclus flexibility allows this
transition to be examined.  The facilities used in these simulations are:

@@

    \item \textbf{Reactor} (\Class{cycamore::Reactor}): This is a reactor
        model that requests any number of input fuel types and transmutes them
        to static compositions when they are burnt and discharged from the
        core.  . The reactor was configured to model a light water reactor
        with a 3 batch core (20,000 kg HM per batch) operating on an 18 month
        cycle with a 2 month refuel time.  The reactor was also configured to
        take in either enriched UOX fuel or recycled MOX fuel - preferring the
        latter if available.

    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
        facility requests depleted uranium and separated fissile material and
        mixes them together into recycled MOX fuel that it offers to
        requesters.  The two streams are mixed in a ratio in order to match
        simple neutronics properties of the target fuel as closely as
        possible.  The method used is based on a variation "equivalence
        method" originally developed by Baker and Ross
        \cite{baker1963comparison}.  This technique has also been used in the
        Commelini-Sicart (COSI) fuel cycle simulator developed by the French
        Commissariat \`{a} l'\'{e}nergie atomique (CEA).

@@

    \item \textbf{UOX Fabrication} (\Class{cycamore::Source}): This facility
        provides enriched UOX fuel as requested.  This facility has infinite
        production capacity.

    \item \textbf{DU Source} (\Class{cycamore::Source}): This facility
        provides depleted uranium as requested. This facility has infinite
        production capacity.

@@

For the once through case, the \Class{Reactor} was set to offer all spent fuel
as waste.  For the 1-pass recycle case, the \Class{Reactor} offered spent UOX
into a spent fuel market where it is preferentially sent to separations, but
spent MOX is still offered as waste.  In the infinite-pass recycle case, the
\Class{Reactor} offers all spent fuel into a spent fuel market. Because the
separations facility requests spent fuel with a higher preference than the
repository, it is sent there if possible.  All these preferences are easy to
adjust and \Cyclus will dynamically handle supply constraints and non-uniform
preference resolution.  It is notable that separations and recycle fuel
fabrication capacity is deployed identically in all simulations.  In the
once-through case, the recycling loop never acquires material, and so reactors
always receive fresh UOX fuel.  In the 1-pass recycle case, the recycle loop
only acquires spent UOX.  The \gls{DRE} ensures everything operates smoothly
in all cases.

Cyclus' discrete materials make single-pass recycle easy to implement.  The
reactors keep track of fuel as discrete batches. A reactor remembers where it
received each batch from.  If a batch was received from the recycled fuel
fabrication facility, it does not offer it to separations and instead sends it
to the repository directly.  The material flows for the 1-pass recycle case are
shown in Figure \ref{fig:flowmodopen}.

\begin{figure}[H]
\begin{center}
\includegraphics{./images/flow-mod-open-1.eps}
\end{center}
\caption{1-pass \gls{MOX} recycle scenario material flows.}
\label{fig:flowmodopen}
\end{figure}

Changing the scenario from a 1-pass fuel cycle to an infinite-pass fuel cycle
requires only a one-word change in the input file regarding the output
commodity for the spent \gls{MOX} fuel of the \Class{Reactor}:

\begin{lstlisting}[language=diff]
     <fuel>         
       <incommodity>mox</incommodity>
  -    <outcommodity>waste</outcommodity>
  +    <outcommodity>spent_fuel</outcommodity>
       <inrecipe>mox_fresh_fuel</inrecipe>
       <outrecipe>mox_spent_fuel</outrecipe>
     </fuel>
\end{lstlisting}

This results in the material flows in Figure \ref{fig:flowclosed}.  A
similarly trivial change was used to switch from the once through to a 1-pass
fuel cycle.  Note that the \Class{Reactor} always transmutes fuel into fixed
compositions, the error in isotopic compositions is larger in the
infinite-pass recycle case.

@@

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for once
through (no recycle), 1-pass recycle, and infinite-pass recycle variations of
the one-reactor scenario described above. The figure was generated directly
from \Cyclus output data. After several batch cycles (near month 300) in the
1-pass and inifinite-pass cases, enough separated fissile material accumulates
in the fuel fabrication facility to generate a full recycled batch.  When this
batch is transmuted, more plutonium is burned than created.  This results in a
drop in the total fuel cycle system plutonium inventory.  This pattern repeats
roughly every 10 cycles (200 months) for the 1-pass recycle case and every 9
cycles (180 months) for the infinite-pass recycle case.  Because the 1-pass
recycle scenario does not re-recycle material, it takes the fabrication
facility 2 cycles longer to accumulate a full batch of fissile material.

@@

Figure \ref{fig:puseriesn} shows plutonium buildup for the 10-reactor
simulations of the once through, 1-pass recycle, and infinite-pass recycle
scenarios.  As the number of reactors (with staggered refueling) increases,
the behavior of the system approaches a more steady average reminiscent of
continuous material flow models.
